Supercritical fluid extraction of essential oil from chamomile seeds: modelling, and parameter estimation

### 2024-02-13 SFE_article_Parameter_Estimation - Chamomile/Sections/Parameter_estimation.tex
13.02

 	\begin{table}[h]
		\adjustbox{max width=\columnwidth}{%
			\begin{tabular}{ lccccccc }
				\hline 
				Parameter		&$k_m$[-] 	& $D_i^R\times10^{-13}$[$m^2/s$] 	& $D_e^M\times10^{-12}$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] \\  \hline
				Lower bound		&0	  		& 0 	  			& 0 				& 0 	   		\\ 
				Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			& $+\infty$ 	\\ 
				Initial guesses	&0.1-10		& $0.1-10$ 			& 0.1-10   			& 0.1-10		\\  \hline
		\end{tabular} }
		\caption{Constraints and initial guess}
		\label{tab:Constraints}
	\end{table}

>>>>

 	\begin{table}[h]
		\adjustbox{max width=\columnwidth}{%
			\begin{tabular}{ lccccccc }
				\hline 
				Parameter		&$k_m$[-] 	& $D_i^R\times10^{-13}$[$m^2/s$] 	& $D_e^M\times10^{-12}$[$m^2/s$]	& $\Upsilon$ [-] \\  \hline
				Lower bound		&0	  		& 0 	  			& 0 				& 0 	   		\\ 
				Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			& $+\infty$ 	\\ 
				Initial guesses	&0.1-10		& $0.1-10$ 			& 0.1-10   			& 0.1-10		\\  \hline
		\end{tabular} }
		\caption{Constraints and initial guess}
		\label{tab:Constraints}
	\end{table}

### 2024-02-13 SFE_article_Parameter_Estimation - Chamomile/Sections/Results_Chamomile.tex
13.02

	Similarly to the previous case, the optimal value of $D_i$ exist, but a unique value for the $D_e^M$ cannot be determined. A little influence of the axial diffusion coefficient can be observed on Figure \ref{fig: Fit_1_Di_Dx} in a width range of values. By selecting $D_e^M$ such it has a low value, the axial diffusion term can be reduced and removed from the model without lost of generality.

@@

	The parameter space of the modified model is characterized by the unique minimum value, which corresponds to the solution of the parameter estimation problem for the experiment 1. The red circle shows the minimum value of the cost function found by the optimizer.

	The remaining experiments are fitted to the modified extraction model in the same way. The results of the parameter estimation for experiments at constant flow rate of $6.67\times 10^{-5}$ [kg/s] and constant temperature of 313 [K] are presented in Figure \ref{fig: Fit_1_4_Di_Dx}.

	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and constant temperature of 313 [K]}
		\label{fig: Fit_1_4_Di_Dx}
	\end{figure}

	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and constant temperature of 303 [K]}
		\label{fig: Fit_5_8_Di_Dx}
	\end{figure}

	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
		\caption{Results of parameter estimation for experiments at $3.34\times 10^{-5}$ [kg/s]}
		\label{fig: Fit_9_12_Di_Dx}
	\end{figure}

>>>>

	Similarly to the previous case, the optimal value of $D_i$ exist, but a unique value for the $D_e^M$ cannot be determined. A little influence of the axial diffusion coefficient can be observed on Figure \ref{fig: Fit_1_Di_Dx} in a width range of values. By selecting $D_e^M$ such it has a low value, the axial diffusion term can be reduced and removed from the model without lost of generality. The model reduction is in agreement with the work of \citet{Rahimi2011}, who worked with the same dataset and obtained Peclet numbers in the range from 290 to 400. Such a high values if Pe suggest that the advection term dominates the mass transfer and the axial diffusion is negligible.

@@

	The parameter space of the modified model is characterized by the unique minimum value, which corresponds to the solution of the parameter estimation problem for the experiment 1. The red circle shows the minimum value of the cost function found by the optimizer. The remaining experiments are fitted to the modified extraction model and results are presented in Figure \ref{fig: Fit_Di_Gamma}. The obtained results show good agreement for almost all the experiments.

	\begin{figure}
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 313 [K]}
			\label{fig: Fit_1_4_Di_Gamma}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 303 [K]}
			\label{fig: Fit_5_8_Di_Gamma}
		\end{subfigure}
		\hfil
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
			\label{fig: Fit_9_12_Di_Gamma}
		\end{subfigure}
		\caption{Parameter estimation results}
		\label{fig: Fit_Di_Gamma}
	\end{figure}

	The results from the parameter estimation are further combined to obtain general correlations, which can be used for modelling of the extraction process at dynamically changing operating conditions. The traditional approach for finding correlations by combining Reynolds, Schmidt and Sherwood numbers is not used here because the axial diffusion rate was considered to be negligible. The proposed correlations shows linear trend between obtained parameters and the Reynolds number $\left(Re = \frac{\rho_f u d_p}{\mu}\right)$, as shown in Figure \ref{fig: Correlations}.

	\begin{figure}
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Di_Re.png}
			\caption{Linear regression $D_i^R$}
			\label{fig: Correlations_Di_Re}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Gamma_Re.png}
			\caption{Linear regression $\Upsilon$}
			\label{fig: Correlations_Gamma_Re}
		\end{subfigure}
		\caption{Parameter estimation results}
		\label{fig: Correlations}
	\end{figure}

### 2024-02-13 SFE_article_Parameter_Estimation - Chamomile/Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
13.02

% ===================================================
% METADATA
% ===================================================
\title[mode=title]{Supercritical fluid extraction of essential oil from chamomile seeds: experiments, modelling, and parameter estimation}                      
\shorttitle{Supercritical fluid extraction of essential oil from chamomile seeds: experiments, modelling, and parameter estimation}

@@

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study investigated the supercritical extraction process of chamomile oil from chamomile seeds. A distributed-parameter model describes the fluid-solid extraction process. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated from the Peng-Robinson equation of state. Key model parameters included partition factor internal and axial diffusion coefficients were determined using maximum likelihood estimation from experimental data, assuming normal error. A set of laboratory experiments was performed in under multiple constant operating conditions: $30 - 40~^\circ C$, $100 - 200$ bar, and $1.33-6.66 \times 10^{-5}$ kg/s.

>>>>

% ===================================================
% METADATA
% ===================================================
\title[mode=title]{Supercritical fluid extraction of essential oil from chamomile seeds: modelling, and parameter estimation}                      
\shorttitle{Supercritical fluid extraction of essential oil from chamomile seeds: modelling, and parameter estimation}

@@

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study investigated the supercritical extraction process of chamomile oil from chamomile seeds. A distributed-parameter model describes the fluid-solid extraction process. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated from the Peng-Robinson equation of state. Key model parameters included partition factor internal and axial diffusion coefficients were determined using maximum likelihood estimation from experimental data, assuming normal error. A set of laboratory experiments was performed in under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.
